Out-of-Sample Comparisons of Overfit Models

### 2014-01-09 paper.tex
Tweak commit references in date field
Finesse summation indices in Lemma A4
This commit tweaks the summation indices in Lemma A4 to make them
easier to follow and closes #30.

% VERSION is generated by a post-commit hook and contains the git
% version info
\IfFileExists{VERSION}{
  \input{VERSION}
  \date{\dinfo\ (version \hinfo)}
  \markright{\dinfo\ (version \hinfo)}
}{}

@@

\begin{lem}\label{lem:a2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
  sequence such that $b_T \to \infty$ and $b_T = o(P)$ and define
  \begin{equation*}
    Z_i = \ZDef.
  \end{equation*}
  Then
  \begin{equation}
    \label{eq:10}
    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
    Z_i^2) \to^p 0.
  \end{equation}
  If Assumptions~\ref{asmp-4} and \ref{asmp-5} also hold and we define
  \begin{gather*}
    Z_{1t} = \varianceTermIIIa, \intertext{and} Z_{2t} =
    \varianceTermIVb,
  \end{gather*}
  then
  \begin{equation}
    \label{eq:12}
    \sum_{t=-P+1}^{2P} (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
  \end{equation}
\end{lem}
\begin{proof}
\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
Since these arguments are similar and our modification is the same for
both, we'll just present the more complicated version,~\eqref{eq:12}.

@@

Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
\begin{align*}
  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
  &\quad+ \sum_{t=r b - P + 1}^{2P} \vtIIIsummand \\
  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
\end{align*}
The proof then holds if we can show that both $U_i$ and $U_i'$ obey
\lln s.  We'll do so by proving that $\{U_i -\E_R U_i,
\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
magnitude indices \citep{Mcl:75}.

For non-negative $m$, we have
\begin{equation*}
U_i - \E_R U_i \in \UFiltration{2i+2m-1},
\end{equation*}
establishing half of the mixingale result trivially.  Now fix $i$ and $m >
0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
for each $t =(2i-2)b_T-P+1,\dots,(2i-1)b_T-P$ and $s =
\max(t+R-b_T,R-\h+1),\dots,\min(t+R+b_T,T)$ such that
\begin{equation*}
 \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
\end{equation*}
and
\begin{equation*}
  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
\end{equation*}
Also define
\begin{equation*}
  Z_{1t}^* = 1/\sqrt{P\gamma} \sum_{l=\vttLower}^{\vttUpper}
  (D_{t,t+l+R}^* - \E_R D_{t,t+l+R}^*)\ W(l/\gamma), \\
\end{equation*}
and
\begin{equation*}
Z_{2t}^* = 1/\sqrt{P\gamma} \sum_{j=\vttLower}^{\vttUpper}
    (D_{t,t+l+R}^* - \E_R D_{t,t+l+R}^*)\ \kernelB{j/\gamma}.
\end{equation*}

@@

And we can finish the proof with the following inequalities:
\begin{align*}
  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
  \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
  D_{t+l+R} - D_{t,t+l+R}^* \rVert_2 W(l/\gamma) \\&
  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma
  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
  = O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
\end{align*}
for some positive $u$.  The same argument holds for $Z_{2t}$.
As a result,
\[
E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma\Big) =
 o(b_T/\gamma) \to 0,
\]
as required.
\end{proof}

>>>>

% VERSION is generated by a post-commit hook and contains the git
% version info
\IfFileExists{VERSION}{
  \input{VERSION}
  \date{\dinfo\ (commit \hinfo)}
  \markright{\dinfo\ (commit \hinfo)}
}{}

@@

\begin{lem}\label{lem:a2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
  \begin{equation*}
    Z_i = \ZDef.
  \end{equation*}
  Then
  \begin{equation}
    \label{eq:10}
    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
    Z_i^2) \to^p 0.
  \end{equation}
  If Assumptions~\ref{asmp-4} and \ref{asmp-5} also hold and we define
  \begin{gather*}
    Z_{1t} = \varianceTermIIIa, \intertext{and} Z_{2t} =
    \varianceTermIVb,
  \end{gather*}
  then
  \begin{equation}
    \label{eq:12}
    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
  \end{equation}
\end{lem}
\begin{proof}
\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
Since these arguments are similar and our modification is the same for
both, we'll just present the more complicated version,~\eqref{eq:12}.

@@

Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
\begin{align*}
  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
  &\quad+ \sum_{t=r b_T - P + R + 1}^{2P+R} \vtIIIsummand \\
  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
\end{align*}
The proof then holds if we can show that both $U_i$ and $U_i'$ obey
\lln s.  We'll do so by proving that $\{U_i -\E_R U_i,
\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
magnitude indices \citep{Mcl:75}.

For non-negative $m$, we have
\begin{equation*}
U_i - \E_R U_i \in \UFiltration{2i+2m-1},
\end{equation*}
establishing half of the mixingale result trivially.  Now fix $i$ and $m >
0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
\begin{equation*}
 \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
\end{equation*}
and
\begin{equation*}
  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
\end{equation*}
Also define
\begin{equation*}
  Z_{1t}^* = (P\gamma)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma), \\
\end{equation*}
and
\begin{equation*}
Z_{2t}^* = (P\gamma)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma}.
\end{equation*}

@@

And we can finish the proof with the following inequalities:
\begin{align*}
  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
  \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma) \\&
  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma
  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
  = O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
\end{align*}
for some positive $u$.  The same argument holds for $Z_{2t}$.
As a result,
\[
E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma\Big) =
 o(b_T/\gamma) \to 0,
\]
as required.
\end{proof}
